On the numerical stability of static Gaussian wave packets

### 2017-08-16 jcp-0-0.tex
paper push

\title{On the numerical instability of Gaussian wave packets} %Title of paper

@@

@@

\section{The naive method}

\section{Expansions over frames of wave packets}

\section{Stiff equations of motion}

@@

\section{Global regularisation}

@@

>>>>

\title{On the numerical stability of static Gaussian wave packets} %Title of paper

@@

\section{Ad-hoc regularisation}

@@

\section{Differential equation formulae and stiffness}

\section{Expansions over wave packets}

{\tt Many wave packets, large number states can be represented, discretised $H$ has large evs, discretised equations of motion are stiff.}

{\tt Why do the least norm expansions of number states have large components near the origin of phase space?}

@@

{\tt Effects on evs, stabilisation of dynamics.}

@@

{\tt Other things go wrong when amplitudes are varied, need to study further.}

### 2017-08-16 semii.tex
paper push

>>>>

Explanation.  Suppose the energy eigenstate~$|E_i〉$ has components along singular directions of~$|A〉$ whose singular values are around~$σ$.  When the matrix~$〈A⁺_λ|H|A〉$ acts on the coefficient vector~$〈A⁺|E_i〉$, the vector is multiplied successively by scalars of size around~$σ$, $E_i$, and~$σ/(σ²+λ²)$, whose product is~$E_i×σ²/(σ²+λ²)$.

Tychonov regularisation effectively turns off the dynamics in the high-energy Hilbert subspace where the singular values of~$|A〉$ are small.  This is why the semi-implicit method becomes stable.
